Exp. 2 Analysis: 2AFC, adults vs. children

### 2020-11-12 analysis/exp2_analysis.Rmd
updated analysis of children's Exp 2 data
finished split-half reliability (of subjects, not trials..)

cd <- rawch %>% filter(Exclude!="Y") %>% 
  dplyr::select(-Version, -Torus0, -Exclude, -Qual1, -Qual2, -Notes, -Note)

@@

# Octahedron   39  p= 0.003
#   pyramid trig prism 
#      0.74       0.26 
# Pentagon   41  p= 0.001
#    bowl pentagon 
#    0.76     0.24 
# Pyramid   41  p= 0.06
# octahedron      torus 
#      0.34       0.66 
# Dumbbell_1   42  p= 0.02
#      bowl octahedron 
#      0.69       0.31 
knitr::kable(trial_tab %>% arrange(relation, desc(adult_target_choice)), digits=2)
```

@@

adult_long <- adult_long %>% rename(ID = ResponseId) %>%
  mutate(Age = "adult") %>%
  select(ID, Age, Trial, choice, drop, target, relation, chose_target)

combo_dat %>% group_by(ID, AgeGroup, relation) %>% # alt, 
  summarize(chose_target=mean(chose_target, na.rm=T)) %>%
  group_by(relation, AgeGroup) %>%
  tidyboot_mean(chose_target) %>%
  ggplot(aes(x=relation, y=mean, fill=AgeGroup)) + geom_bar(stat="identity", position=pos) + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = pos) + 
  geom_hline(aes(yintercept=.5), linetype="dashed") + theme_classic()
```

Still collecting data:

```{r}
hist(cd$Age, main="")
```

>>>>

cd <- rawch %>% filter(Exclude!="Y") %>% 
  dplyr::select(-Version, -Torus0, -Exclude, -Qual1, -Qual2, -Note, -Comments)

@@

# Octahedron   39  p= 0.003
#   pyramid trig prism 
#      0.74       0.26 
# Pentagon   41  p= 0.001
#    bowl pentagon 
#    0.76     0.24 
# Pyramid   41  p= 0.06
# octahedron      torus 
#      0.34       0.66 
# Dumbbell_1   42  p= 0.02
#      bowl octahedron 
#      0.69       0.31 
knitr::kable(trial_tab %>% arrange(relation, desc(adult_target_choice)), digits=2)

langcog::ggcorplot(select(trial_tab, child_target_choice, adult_target_choice, model_target_choice))
```

## Compare Children's and Adult's Choices Per Trial

```{r per-trial-comparison}
adult_long <- adult_long %>% rename(ID = ResponseId) %>%
  mutate(Age = "adult") %>%
  select(ID, Age, Trial, choice, drop, target, relation, chose_target)

combo_dat %>% group_by(drop, target, relation, AgeGroup) %>%
  summarise(chose_target = mean(chose_target, na.rm=T)) %>%
  pivot_wider(names_from = AgeGroup, values_from = chose_target) %>%
  ggplot(aes(x=adult, y=child, group=relation, color=relation)) + 
    geom_point(alpha=.7) + theme_bw() + ylim(0,1) + xlim(0,1) + 
  geom_abline(xintercept=0, slope=1, linetype="dashed") #+
  #geom_text(aes(label=target)) #

```

@@

combo_dat %>% 
  mutate(AgeGroup = ifelse(Age=="adult", "adult", 
                           ifelse(Age=="3" | Age=="4", "3-4 yo", "5-7 yo"))) %>%
  group_by(ID, AgeGroup, relation) %>% # alt, 
  summarize(chose_target=mean(chose_target, na.rm=T)) %>%
  group_by(relation, AgeGroup) %>%
  tidyboot_mean(chose_target) %>%
  ggplot(aes(x=relation, y=mean, fill=AgeGroup)) + geom_bar(stat="identity", position=pos) + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = pos) + 
  geom_hline(aes(yintercept=.5), linetype="dashed") + theme_classic() + ylim(0,1)
```

## Reliability

Check reliability of responses within- and across-conditions (support and containment).

```{r}
# library(psych) # has a (Cronbach's) alpha function that takes a covariance matrix

# split subjects in half, check cor between halves
split_half_subj_cor <- function(dat, nsim=100) {
  subjs = unique(dat$ID)
  cors = rep(NA, nsim)
  for(i in 1:nsim) {
    idx1 = sample(subjs, size=length(subjs)/2)
    idx2 = setdiff(subjs, idx1) # nonsampled items
    h1 <- dat %>% filter(is.element(ID, idx1)) %>% 
      group_by(AgeGroup, Trial) %>%
      summarise(mean = mean(chose_target, na.rm=T), .groups="keep")
    h2 <- dat %>% filter(is.element(ID, idx2)) %>% 
      group_by(AgeGroup, Trial) %>%
      summarise(mean = mean(chose_target, na.rm=T), .groups="keep")
    cors[i] = cor(h1$mean, h2$mean)
  }
  return(cors)
}

# overall
sh_subj = split_half_subj_cor(combo_dat)
mean(sh_subj) # .736

sh_subj_adult = split_half_subj_cor(subset(combo_dat, AgeGroup=="adult"))
mean(sh_subj_adult) # .791

sh_subj_child = split_half_subj_cor(subset(combo_dat, AgeGroup=="child"))
mean(sh_subj_child) # .56

sh_subj_contain = split_half_subj_cor(subset(combo_dat, relation=="contain"))
mean(sh_subj_contain) # .649

sh_subj_support = split_half_subj_cor(subset(combo_dat, relation=="support"))
mean(sh_subj_support) # .619

# split items in half, check cor between halves...GK: I don't think we care about this
split_half_item_cor <- function(dat, nsim=100) {
  trials = unique(dat$Trial)
  cors = rep(NA, nsim)
  for(i in 1:nsim) {
    idx1 = sample(trials, size=length(trials)/2)
    idx2 = setdiff(trials, idx1) # nonsampled items
    # h1 <- dat %>% filter(is.element(idx1, Trials)) %>% group_by(ID, AgeGroup)

    cors[i] = cor()
  }
  return(cors)
}

```
